### 2015-08-02 doc/manual/installation.tex
Added profiles examples
Updated make test to remove distinction between small and large examples

Next, to compile, go to the directory {\ttfamily sfincs/fortran/version3/} and run {\ttfamily make}.

@@

To test that your \sfincs~executable is working, you can run {\ttfamily make test}
from the \path{sfincs/fortran/version3/} directory.  Doing so will run
\sfincs~for some or all of the examples in the {\ttfamily sfincs/fortran/version3/examples/} directories.
(The runs will be performed in series if no queueing system is available, otherwise the runs will all
be submitted to the queueing system.)
After each example completes, several of the output quantities (such as parallel flows and radial fluxes)
will be checked, using the
{\ttfamily tests\_small.py} or {\ttfamily tests\_large.py} script in the example's directory.

If you run {\ttfamily make retest} from the \path{sfincs/fortran/version3/} directory,
no new runs of \sfincs~will be performed, but the {\ttfamily tests\_small.py} or {\ttfamily tests\_large.py} script
will be run on any existing {\ttfamily sfincsOutput.h5} files in the \path{sfincs/fortran/version3/examples/} directories.

The {\ttfamily make test} functionality relies on system-specific commands in the
\path{sfincs/fortran/version3/makefiles/makefile.SFINCS_SYSTEM} file.  If you experience
problems with  {\ttfamily make test}, it is likely that this file needs modification.

>>>>

Next, to compile, go to the directory {\ttfamily sfincs/fortran/version3/} and run {\ttfamily make -j}.
(The {\ttfamily -j} flag means compiliation will be done in parallel, i.e. faster.)

@@

To test that your \sfincs~executable is working, you can run {\ttfamily make test}
from the \path{sfincs/fortran/version3/} directory.  Doing so will run
\sfincs~for some or all of the examples in the {\ttfamily sfincs/fortran/version3/examples/} directories.
(The runs will be performed in series if no queueing system is available, otherwise the runs will all
be submitted to the queueing system.)
After each example completes, several of the output quantities (such as parallel flows and radial fluxes)
will be checked, using the
{\ttfamily tests.py} script in the example's directory.

If you run {\ttfamily make retest} from the \path{sfincs/fortran/version3/} directory,
no new runs of \sfincs~will be performed, but the {\ttfamily tests.py} script
will be run on any existing {\ttfamily sfincsOutput.h5} files in the \path{sfincs/fortran/version3/examples/} directories.

The {\ttfamily make test} functionality relies on several environment variables set in the
\path{sfincs/fortran/version3/makefiles/makefile.SFINCS_SYSTEM} file, as well as on the
\path{job.SFINCS_SYSTEM} files in each example subdirectory.  If you experience
problems with  {\ttfamily make test}, there is a good chance that one of these files needs modification.
